TEMPERATURES AND METALLICITIES OF M DWARFS IN THE \apogee\ SURVEY

### 2019-07-31 paper/draft.tex
table formatting

\begin{deluxetable}{|c|c|c|c|c|}
\tablecaption{Strong $\teff$-correlated molecular lines for all features with significance greater than $2\sigma_{\rm jackknife}$.}
\tablehead{Species & Wavelength & Derivative & $\sigma_{\rm jackknife}$ & Significance}
	\startdata
	FeH & 16107.127 & -0.002 & 0.001 & -2.78 \\
	FeH & 16245.463 & -0.005 & 0.002 & -3.214 \\
	FeH & 16271.519 & -0.002 & 0.001 & -2.013 \\
	FeH & 16284.562 & -0.006 & 0.001 & -5.807 \\
	FeH & 16377.066 & -0.005 & 0.001 & -4.554 \\
	FeH & 16741.489 & -0.002 & 0.001 & -2.873 \\
	FeH & 16812.415 & -0.004 & 0.001 & -4.241 \\
	FeH & 16813.808 & -0.006 & 0.001 & -3.954 \\
	FeH & 16922.405 & -0.003 & 0.001 & -3.867 \\
	FeH & 16934.801 & -0.004 & 0.001 & -3.591 \\
	OH & 15278.267 & 0.006 & 0.003 & 2.47 \\
	OH & 15280.8 & 0.004 & 0.002 & 2.007 \\
	OH & 15391.186 & 0.006 & 0.003 & 2.127 \\
	OH & 15407.355 & 0.01 & 0.002 & 4.836 \\
	OH & 15409.271 & 0.008 & 0.002 & 4.683 \\
	OH & 15505.797 & 0.009 & 0.003 & 3.511 \\
	OH & 15560.305 & 0.008 & 0.002 & 3.865 \\
	OH & 15565.895 & 0.005 & 0.002 & 2.505 \\
	OH & 15568.691 & 0.007 & 0.001 & 4.929 \\
	OH & 15572.133 & 0.008 & 0.002 & 4.393 \\
	OH & 16052.7 & 0.008 & 0.002 & 3.517 \\
	OH & 16055.362 & 0.006 & 0.002 & 3.7 \\
	OH & 16061.796 & 0.007 & 0.003 & 2.502 \\
	OH & 16065.124 & 0.009 & 0.002 & 4.214 \\
	OH & 16069.564 & 0.008 & 0.003 & 3.275 \\
	OH & 16074.227 & 0.007 & 0.002 & 3.338 \\
	OH & 16190.345 & 0.007 & 0.003 & 2.498 \\
	OH & 16192.134 & 0.008 & 0.002 & 4.012 \\
	OH & 16203.995 & 0.006 & 0.002 & 3.039 \\
	OH & 16207.129 & 0.004 & 0.002 & 2.196 \\
	OH & 16352.196 & 0.007 & 0.002 & 3.609 \\
	OH & 16354.682 & 0.011 & 0.003 & 4.167 \\
	OH & 16364.626 & 0.007 & 0.003 & 2.661 \\
	OH & 16368.244 & 0.008 & 0.002 & 4.303 \\
	OH & 16581.281 & 0.008 & 0.002 & 4.41 \\
	OH & 16581.74 & 0.004 & 0.001 & 4.842 \\
	OH & 16866.621 & 0.005 & 0.001 & 3.169 \\
	OH & 16871.982 & 0.012 & 0.002 & 4.892 \\
	OH & 16878.976 & 0.006 & 0.002 & 3.807 \\
	OH & 16884.573 & 0.005 & 0.002 & 3.066 \\
	OH & 16886.206 & 0.006 & 0.001 & 5.131 \\
	OH & 16895.074 & 0.005 & 0.002 & 2.197 \\
	\nodata & \nodata & \nodata & \nodata & \nodata
	\enddata
\end{deluxetable} \label{table:teff_derivative}

\begin{deluxetable}{|c|c|c|c|c|}
\tablecaption{Strong $\teff$-correlated atomic lines for all features with significance greater than $2\sigma_{\rm jackknife}$.}
\tablehead{Species & Wavelength & Derivative & $\sigma_{\rm jackknife}$ & Significance}
	\startdata
	\nodata & \nodata & \nodata & \nodata & \nodata \\
	Fe I & 15207.509 & -0.007 & 0.003 & -2.622 \\
	Fe I & 15648.478 & -0.006 & 0.002 & -3.273 \\
	Fe I & 15692.643 & -0.008 & 0.002 & -4.056 \\
	Si I & 15960.044 & -0.009 & 0.004 & -2.523 \\
	Si I & 16094.893 & -0.014 & 0.003 & -4.368 \\
	Si I & 16680.77 & -0.01 & 0.003 & -3.475 \\
	K I & 15162.824 & -0.006 & 0.002 & -2.294 \\
	Ti I & 15715.641 & 0.006 & 0.002 & 2.894 \\
	Ti I & 16634.973 & 0.003 & 0.001 & 4.224 \\
	V I & 15923.924 & 0.003 & 0.001 & 3.6 \\
	Mn I & 15159.054 & -0.006 & 0.002 & -3.123 \\
	\enddata
\end{deluxetable}

\begin{deluxetable}{|c|c|c|c|c|}
\tablecaption{Strong $\feh$-correlated atomic and molecular lines for all features with significance greater than $2\sigma_{\rm jackknife}$.}
\tablehead{Species & Wavelength & Derivative & $\sigma_{\rm jackknife}$ & Significance}
	\startdata
	FeH & 16114.027 & 0.004 & 0.001 & 2.673 \\
	FeH & 16574.64 & 0.003 & 0.001 & 2.356 \\
	FeH & 16694.372 & 0.003 & 0.001 & 2.193 \\
	FeH & 16814.041 & 0.004 & 0.002 & 2.513 \\
	OH & 16052.7 & 0.005 & 0.002 & 2.034 \\
	OH & 16055.362 & 0.006 & 0.002 & 2.805 \\
	OH & 16065.124 & 0.007 & 0.003 & 2.364 \\
	OH & 16871.982 & 0.007 & 0.003 & 2.306 \\
	OH & 16886.206 & 0.004 & 0.001 & 2.52 \\
	Fe I & 15490.381 & -0.004 & 0.001 & -2.722 \\
	Fe I & 15692.643 & -0.005 & 0.002 & -2.759 \\
	Fe I & 16009.512 & -0.006 & 0.003 & -2.143 \\
	Si I & 15960.044 & -0.007 & 0.003 & -2.112 \\
	Si I & 16680.77 & -0.006 & 0.003 & -2.156 \\
	K I & 15163.033 & 0.006 & 0.003 & 2.043 \\
	V I & 15923.924 & 0.002 & 0.001 & 2.017 \\
	Cr I & 15680.073 & -0.005 & 0.002 & -2.811 \\
	Mn I & 15159.054 & -0.008 & 0.002 & -3.298 \\
	Mn I & 15262.023 & -0.005 & 0.002 & -2.996 \\
	\enddata
\end{deluxetable} \label{table:feh_derivative}

@@

\begin{deluxetable*}{cccccccc}
\tablecaption{Metallicities of \apogee\ M dwarfs with wide binaries. Reported in this table are the ASPCAP [M/H] and \cannon\ [Fe/H] of the M dwarfs, as well as the metallicity values of their binary companions. The source/survey of the metallicity and spectral classes of the companions are also given. \label{table:binaries}}
\tabletypesize{\scriptsize}
\tablehead{Mdwarf Gaia ID      & Companion Gaia ID   & Mdwarf [M/H] & Mdwarf [Fe/H] & Companion [Fe/H] & Companion source & Separation (AU)}
	\startdata
	1476768433933264128 & 1476762627137479552 & -0.18      & 0.01        & 0.10           & APOGEE Cannon M   & 16091      \\
	1476646285062821888 & 1476646250703083264 & -0.02      & 0.18        & 0.27           & APOGEE Cannon M   & 4155       \\
	4008743154907642496 & 4008743086188165248 & -0.20      & 0.02        & 0.09           & APOGEE Cannon M   & 11855      \\
	3053911383155592832 & 3053907221325174144 & -0.25      & -0.15       & -0.15          & APOGEE Cannon M   & 12884      \\
	1475867727751525632 & 1475867727751525504 & -0.25      & -0.15       & -0.13          & APOGEE Cannon M   & 5091       \\
	933708229245319552  & 933708164821511424  & -0.23      & 0.11        & 0.01           & APOGEE Cannon M   & 2245       \\
	3888520938618496768 & 3888520938618115456 & -0.16      & -0.15       & -0.14          & APOGEE Cannon M   & 1128       \\
	3888309828090932608 & 3888309832385988992 & -0.24      & -0.01       & 0.04           & APOGEE Cannon M   & 2499       \\
	374137560388179328  & 374137560388178304  & -0.34      & -0.24       & -0.34          & LAMOST FGK        & 5888       \\
	4031346880591589248 & 4031346914951327104 & -0.33      & -0.25       & -0.18          & LAMOST FGK        & 6637       \\
	3443427533502334592 & 3443427533502335744 & 0.06       & 0.20        & 0.32           & LAMOST FGK        & 3151       \\
	1605991802162861696 & 1605991767803123200 & -0.16      & -0.03       & -0.06          & LAMOST FGK        & 1043       \\
	4418850890305439872 & 4418851263967008000 & -0.18      & 0.11        & 0.27           & APOGEE ASPCAP FGK & 4920       \\
	1381455722290898176 & 1381408782592655616 & -0.13      & -0.02       & -0.08          & APOGEE ASPCAP FGK & 2401       \\
	2687603208839189376 & 2687603311918406528 & -0.12      & 0.00        & -0.03          & APOGEE ASPCAP FGK & 11201    
	\enddata
\end{deluxetable*}

@@

\begin{deluxetable*}{rcl}
\tablecaption{Test results table header description.}
\tablehead{Column & Unit & Description}
	\startdata
	{\tt APOGEE$\_$ID} 	& 	& \apogee\ \zmass\ designation \\
	{\tt GAIA$\_$ID} 		&	& \gaia\ identification number \\
	{\tt TEFF} 				& K	& Mann-trained \cannon\ effective temperature	\\
	{\tt FE$\_$H }		& dex	& Mann-trained \cannon\ $\feh$	\\
	{\tt SPT} 				& 	& West-trained \cannon\ spectral subtype (M0$-$M9)	\\
	{\tt CHI$\_$MANN} 	& 	& $\chi^2$ fit of Mann-trained \cannon\ model	\\
	{\tt CHI$\_$WEST} 	& 	& $\chi^2$ fit of West-trained \cannon\ model	\\
	{\tt RADIUS} 			& R$_\odot$	& Radius determined by \citealt{Mann:2015} relation	\\
	{\tt MASS} 			& M$_\odot$	& Mass determined by \citealt{Mann:2019} relation	\\
	{\tt J} 				& mag	& \apogee\ $J$ band photometry	\\
	{\tt J$\_$ERR} 		& mag	& \apogee\ $J$ band photometry uncertainty	\\
	{\tt H} 				& mag	& \apogee\ $H$ band photometry	\\
	{\tt H$\_$ERR} 		& mag	& \apogee\ $H$ band photometry uncertainty	\\
	{\tt K} 				& mag	& \apogee\ $K$ band photometry	\\
	{\tt K$\_$ERR} 		& mag	& \apogee\ $K$ band photometry uncertainty	\\
	{\tt BP$\_$MAG }		& mag	& \gaia\ $BP$ band photometry	\\
	{\tt RP$\_$MAG} 		& mag	& \gaia\ $RP$ band photometry	\\
	{\tt G$\_$MAG} 		& mag	& \gaia\ $G$ band photometry	\\
	{\tt G$\_$ABS} 		& mag	& \gaia\ $G$ band absolute magnitude	\\
	{\tt BP$\_$RP} 		& mag	& \gaia\ $BP-RP$ color	\\
	{\tt RA} 				& deg	& \apogee\ radial ascension angle	\\
	{\tt DEC} 			& deg	& \apogee\ declination angle	\\
	{\tt PMRA} 			& mas yr$^{-1}$	& \gaia\ radial ascension proper motion	\\
	{\tt PMRA$\_$ERR} 	& mas yr$^{-1}$	& \gaia\ radial ascension proper motion uncertainty	\\
	{\tt PMDEC} 			& mas yr$^{-1}$	& \gaia\ declination proper motion	\\
	{\tt PMDEC$\_$ERR} 	& mas yr$^{-1}$	& \gaia\ declination proper motion uncertainty	\\
	{\tt PLX} 			& mas	& \gaia\ parallax	\\
	{\tt PLX$\_$ERR} 		& mas	& \gaia\ parallax uncertainty	\\
	{\tt DIST} 			& pc	& Distance (1/$\varpi$)	\\
	{\tt RV$\_$APOGEE} 	& km s$^{-1}$	& \apogee\ radial velocity	\\
	{\tt RV$\_$APOGEE$\_$ERR} 	& km s$^{-1}$	& \apogee\ radial velocity uncertainty	\\
	{\tt RV$\_$GAIA} 				& km s$^{-1}$	& \gaia\ radial velocity	\\
	{\tt RV$\_$GAIA$\_$ERR}		& km s$^{-1}$	& \gaia\ radial velocity uncertainty	\\
	{\tt Vx} 				& km s$^{-1}$	& Cartesian $x$ velocity in Galactocentric coordnates	\\
	{\tt Vy} 				& km s$^{-1}$	& Cartesian $y$ velocity in Galactocentric coordnates	\\
	{\tt Vz} 				& km s$^{-1}$	& Cartesian $z$ velocity in Galactocentric coordnates	\\
	{\tt X} 				& pc	& Cartesian $x$ position in Galactocentric coordnates	\\
	{\tt Y} 				& pc	& Cartesian $y$ position in Galactocentric coordnates	\\
	{\tt Z} 				& pc	& Cartesian $z$ position in Galactocentric coordnates	
\enddata
\end{deluxetable*} \label{table:test_results}

>>>>

\begin{deluxetable}{ccccc}
\tablecaption{Strong $\teff$-correlated molecular lines for all features with significance greater than $2\sigma_{\rm jackknife}$.}
\tablehead{\colhead{Species} & \colhead{Wavelength} & \colhead{Derivative} & \colhead{$\sigma_{\rm jackknife}$} & \colhead{Significance}}
	\startdata
	FeH & 16107.127 & -0.002 & 0.001 & -2.78 \\
	FeH & 16245.463 & -0.005 & 0.002 & -3.214 \\
	FeH & 16271.519 & -0.002 & 0.001 & -2.013 \\
	FeH & 16284.562 & -0.006 & 0.001 & -5.807 \\
	FeH & 16377.066 & -0.005 & 0.001 & -4.554 \\
	FeH & 16741.489 & -0.002 & 0.001 & -2.873 \\
	FeH & 16812.415 & -0.004 & 0.001 & -4.241 \\
	FeH & 16813.808 & -0.006 & 0.001 & -3.954 \\
	FeH & 16922.405 & -0.003 & 0.001 & -3.867 \\
	FeH & 16934.801 & -0.004 & 0.001 & -3.591 \\
	OH & 15278.267 & 0.006 & 0.003 & 2.47 \\
	OH & 15280.8 & 0.004 & 0.002 & 2.007 \\
	OH & 15391.186 & 0.006 & 0.003 & 2.127 \\
	OH & 15407.355 & 0.01 & 0.002 & 4.836 \\
	OH & 15409.271 & 0.008 & 0.002 & 4.683 \\
	OH & 15505.797 & 0.009 & 0.003 & 3.511 \\
	OH & 15560.305 & 0.008 & 0.002 & 3.865 \\
	OH & 15565.895 & 0.005 & 0.002 & 2.505 \\
	OH & 15568.691 & 0.007 & 0.001 & 4.929 \\
	OH & 15572.133 & 0.008 & 0.002 & 4.393 \\
	OH & 16052.7 & 0.008 & 0.002 & 3.517 \\
	OH & 16055.362 & 0.006 & 0.002 & 3.7 \\
	OH & 16061.796 & 0.007 & 0.003 & 2.502 \\
	OH & 16065.124 & 0.009 & 0.002 & 4.214 \\
	OH & 16069.564 & 0.008 & 0.003 & 3.275 \\
	OH & 16074.227 & 0.007 & 0.002 & 3.338 \\
	OH & 16190.345 & 0.007 & 0.003 & 2.498 \\
	OH & 16192.134 & 0.008 & 0.002 & 4.012 \\
	OH & 16203.995 & 0.006 & 0.002 & 3.039 \\
	OH & 16207.129 & 0.004 & 0.002 & 2.196 \\
	OH & 16352.196 & 0.007 & 0.002 & 3.609 \\
	OH & 16354.682 & 0.011 & 0.003 & 4.167 \\
	OH & 16364.626 & 0.007 & 0.003 & 2.661 \\
	OH & 16368.244 & 0.008 & 0.002 & 4.303 \\
	OH & 16581.281 & 0.008 & 0.002 & 4.41 \\
	OH & 16581.74 & 0.004 & 0.001 & 4.842 \\
	OH & 16866.621 & 0.005 & 0.001 & 3.169 \\
	OH & 16871.982 & 0.012 & 0.002 & 4.892 \\
	OH & 16878.976 & 0.006 & 0.002 & 3.807 \\
	OH & 16884.573 & 0.005 & 0.002 & 3.066 \\
	OH & 16886.206 & 0.006 & 0.001 & 5.131 \\
	OH & 16895.074 & 0.005 & 0.002 & 2.197 \\
	\nodata & \nodata & \nodata & \nodata & \nodata
	\enddata
\end{deluxetable} \label{table:teff_derivative}

\begin{deluxetable}{ccccc}
\tablecaption{Strong $\teff$-correlated atomic lines for all features with significance greater than $2\sigma_{\rm jackknife}$.}
\tablehead{\colhead{Species} & \colhead{Wavelength} & \colhead{Derivative} & \colhead{$\sigma_{\rm jackknife}$} & \colhead{Significance}}
	\startdata
	\nodata & \nodata & \nodata & \nodata & \nodata \\
	Fe I & 15207.509 & -0.007 & 0.003 & -2.622 \\
	Fe I & 15648.478 & -0.006 & 0.002 & -3.273 \\
	Fe I & 15692.643 & -0.008 & 0.002 & -4.056 \\
	Si I & 15960.044 & -0.009 & 0.004 & -2.523 \\
	Si I & 16094.893 & -0.014 & 0.003 & -4.368 \\
	Si I & 16680.77 & -0.01 & 0.003 & -3.475 \\
	K I & 15162.824 & -0.006 & 0.002 & -2.294 \\
	Ti I & 15715.641 & 0.006 & 0.002 & 2.894 \\
	Ti I & 16634.973 & 0.003 & 0.001 & 4.224 \\
	V I & 15923.924 & 0.003 & 0.001 & 3.6 \\
	Mn I & 15159.054 & -0.006 & 0.002 & -3.123 \\
	\enddata
\end{deluxetable}

\begin{deluxetable}{ccccc}
\tablecaption{Strong $\feh$-correlated atomic and molecular lines for all features with significance greater than $2\sigma_{\rm jackknife}$.}
\tablehead{\colhead{Species} & \colhead{Wavelength} & \colhead{Derivative} & \colhead{$\sigma_{\rm jackknife}$} & \colhead{Significance}}
	\startdata
	FeH & 16114.027 & 0.004 & 0.001 & 2.673 \\
	FeH & 16574.64 & 0.003 & 0.001 & 2.356 \\
	FeH & 16694.372 & 0.003 & 0.001 & 2.193 \\
	FeH & 16814.041 & 0.004 & 0.002 & 2.513 \\
	OH & 16052.7 & 0.005 & 0.002 & 2.034 \\
	OH & 16055.362 & 0.006 & 0.002 & 2.805 \\
	OH & 16065.124 & 0.007 & 0.003 & 2.364 \\
	OH & 16871.982 & 0.007 & 0.003 & 2.306 \\
	OH & 16886.206 & 0.004 & 0.001 & 2.52 \\
	Fe I & 15490.381 & -0.004 & 0.001 & -2.722 \\
	Fe I & 15692.643 & -0.005 & 0.002 & -2.759 \\
	Fe I & 16009.512 & -0.006 & 0.003 & -2.143 \\
	Si I & 15960.044 & -0.007 & 0.003 & -2.112 \\
	Si I & 16680.77 & -0.006 & 0.003 & -2.156 \\
	K I & 15163.033 & 0.006 & 0.003 & 2.043 \\
	V I & 15923.924 & 0.002 & 0.001 & 2.017 \\
	Cr I & 15680.073 & -0.005 & 0.002 & -2.811 \\
	Mn I & 15159.054 & -0.008 & 0.002 & -3.298 \\
	Mn I & 15262.023 & -0.005 & 0.002 & -2.996 \\
	\enddata
\end{deluxetable} \label{table:feh_derivative}

@@

\begin{deluxetable*}{cccccccc}
\tablecaption{Metallicities of \apogee\ M dwarfs with wide binaries. Reported in this table are the ASPCAP [M/H] and \cannon\ [Fe/H] of the M dwarfs, as well as the metallicity values of their binary companions. The source/survey of the metallicity and spectral classes of the companions are also given. \label{table:binaries}}
\tabletypesize{\scriptsize} 
\tablehead{\colhead{Mdwarf Gaia ID}      & \colhead{Companion Gaia ID}   & \colhead{Mdwarf [M/H]} & \colhead{Mdwarf [Fe/H]} & \colhead{Companion [Fe/H]} & \colhead{Companion source} & \colhead{Separation (AU)}}
	\startdata
	1476768433933264128 & 1476762627137479552 & -0.18      & 0.01        & 0.10           & APOGEE Cannon M   & 16091      \\
	1476646285062821888 & 1476646250703083264 & -0.02      & 0.18        & 0.27           & APOGEE Cannon M   & 4155       \\
	4008743154907642496 & 4008743086188165248 & -0.20      & 0.02        & 0.09           & APOGEE Cannon M   & 11855      \\
	3053911383155592832 & 3053907221325174144 & -0.25      & -0.15       & -0.15          & APOGEE Cannon M   & 12884      \\
	1475867727751525632 & 1475867727751525504 & -0.25      & -0.15       & -0.13          & APOGEE Cannon M   & 5091       \\
	933708229245319552  & 933708164821511424  & -0.23      & 0.11        & 0.01           & APOGEE Cannon M   & 2245       \\
	3888520938618496768 & 3888520938618115456 & -0.16      & -0.15       & -0.14          & APOGEE Cannon M   & 1128       \\
	3888309828090932608 & 3888309832385988992 & -0.24      & -0.01       & 0.04           & APOGEE Cannon M   & 2499       \\
	374137560388179328  & 374137560388178304  & -0.34      & -0.24       & -0.34          & LAMOST FGK        & 5888       \\
	4031346880591589248 & 4031346914951327104 & -0.33      & -0.25       & -0.18          & LAMOST FGK        & 6637       \\
	3443427533502334592 & 3443427533502335744 & 0.06       & 0.20        & 0.32           & LAMOST FGK        & 3151       \\
	1605991802162861696 & 1605991767803123200 & -0.16      & -0.03       & -0.06          & LAMOST FGK        & 1043       \\
	4418850890305439872 & 4418851263967008000 & -0.18      & 0.11        & 0.27           & APOGEE ASPCAP FGK & 4920       \\
	1381455722290898176 & 1381408782592655616 & -0.13      & -0.02       & -0.08          & APOGEE ASPCAP FGK & 2401       \\
	2687603208839189376 & 2687603311918406528 & -0.12      & 0.00        & -0.03          & APOGEE ASPCAP FGK & 11201    
	\enddata
\end{deluxetable*}

@@

\begin{deluxetable*}{rcl}
\tablecaption{Test results table header description.}
\tablehead{\colhead{Column} & \colhead{Unit} & \colhead{Description}}
	\startdata
	{\tt APOGEE$\_$ID} 	& 	& \apogee\ \zmass\ designation \\
	{\tt GAIA$\_$ID} 		&	& \gaia\ identification number \\
	{\tt TEFF} 				& K	& Mann-trained \cannon\ effective temperature	\\
	{\tt FE$\_$H }		& dex	& Mann-trained \cannon\ $\feh$	\\
	{\tt SPT} 				& 	& West-trained \cannon\ spectral subtype (M0$-$M9)	\\
	{\tt CHI$\_$MANN} 	& 	& $\chi^2$ fit of Mann-trained \cannon\ model	\\
	{\tt CHI$\_$WEST} 	& 	& $\chi^2$ fit of West-trained \cannon\ model	\\
	{\tt RADIUS} 			& R$_\odot$	& Radius determined by \citealt{Mann:2015} relation	\\
	{\tt MASS} 			& M$_\odot$	& Mass determined by \citealt{Mann:2019} relation	\\
	{\tt J} 				& mag	& \apogee\ $J$ band photometry	\\
	{\tt J$\_$ERR} 		& mag	& \apogee\ $J$ band photometry uncertainty	\\
	{\tt H} 				& mag	& \apogee\ $H$ band photometry	\\
	{\tt H$\_$ERR} 		& mag	& \apogee\ $H$ band photometry uncertainty	\\
	{\tt K} 				& mag	& \apogee\ $K$ band photometry	\\
	{\tt K$\_$ERR} 		& mag	& \apogee\ $K$ band photometry uncertainty	\\
	{\tt BP$\_$MAG }		& mag	& \gaia\ $BP$ band photometry	\\
	{\tt RP$\_$MAG} 		& mag	& \gaia\ $RP$ band photometry	\\
	{\tt G$\_$MAG} 		& mag	& \gaia\ $G$ band photometry	\\
	{\tt G$\_$ABS} 		& mag	& \gaia\ $G$ band absolute magnitude	\\
	{\tt BP$\_$RP} 		& mag	& \gaia\ $BP-RP$ color	\\
	{\tt RA} 				& deg	& \apogee\ radial ascension angle	\\
	{\tt DEC} 			& deg	& \apogee\ declination angle	\\
	{\tt PMRA} 			& mas yr$^{-1}$	& \gaia\ radial ascension proper motion	\\
	{\tt PMRA$\_$ERR} 	& mas yr$^{-1}$	& \gaia\ radial ascension proper motion uncertainty	\\
	{\tt PMDEC} 			& mas yr$^{-1}$	& \gaia\ declination proper motion	\\
	{\tt PMDEC$\_$ERR} 	& mas yr$^{-1}$	& \gaia\ declination proper motion uncertainty	\\
	{\tt PLX} 			& mas	& \gaia\ parallax	\\
	{\tt PLX$\_$ERR} 		& mas	& \gaia\ parallax uncertainty	\\
	{\tt DIST} 			& pc	& Distance (1/$\varpi$)	\\
	{\tt RV$\_$APOGEE} 	& km s$^{-1}$	& \apogee\ radial velocity	\\
	{\tt RV$\_$APOGEE$\_$ERR} 	& km s$^{-1}$	& \apogee\ radial velocity uncertainty	\\
	{\tt RV$\_$GAIA} 				& km s$^{-1}$	& \gaia\ radial velocity	\\
	{\tt RV$\_$GAIA$\_$ERR}		& km s$^{-1}$	& \gaia\ radial velocity uncertainty	\\
	{\tt Vx} 				& km s$^{-1}$	& Cartesian $x$ velocity in Galactocentric coordnates	\\
	{\tt Vy} 				& km s$^{-1}$	& Cartesian $y$ velocity in Galactocentric coordnates	\\
	{\tt Vz} 				& km s$^{-1}$	& Cartesian $z$ velocity in Galactocentric coordnates	\\
	{\tt X} 				& pc	& Cartesian $x$ position in Galactocentric coordnates	\\
	{\tt Y} 				& pc	& Cartesian $y$ position in Galactocentric coordnates	\\
	{\tt Z} 				& pc	& Cartesian $z$ position in Galactocentric coordnates	
\enddata
\end{deluxetable*} \label{table:test_results}
